\section{INTRODUCTION}
CI/CD is a development method used to efficiently build and test code updates. 
It helps organizations keep their software consistent and allows them to smoothly 
incorporate new changes. However, CI/CD systems can be tempting targets for cyberattackers. 
These attackers may try to insert malicious code into CI/CD processes, 
steal valuable credentials, or disrupt the original functioning of applications\cite{sonatype2020}.

Recent incidence like the infection of SolarWind's Orion platform \cite{ladisa2023sok, 
peisert2021perspectives} which is used to monitor and manage the network is downloaded by 
thousands of customers, including U.S. government agencies, critical infrastructure providers, 
and private companies. 

Another malicious attack target the credentials from a contributor of the esline-scope package.
The attackers updated the malicious code within the code base, which will end up stealing
multiple credentials from the downstream users \cite{eslint2018}.

Sometimes, the risks are due to the situation that the consumers are not aware of the importance 
of frequent update of the dependencies which are consumed in their packages. In this situation,
the attackers is able to discover the unsafe dependencies on the git repositories, then looking for
other packages depend on these unsafe outdated dependencies. It is simple to find out how the bugs being
fixed on the original dependencies' repositories, and directly compromise the downstream users with the bugs.
Therefore, a smart alert system~\cite{wang2020empirical} to detect if the older version contains
bugs and should be updated. Then, the system will automatically update the dependencies. This system can be deployed
in different stages to automatically detect unsafe version, and update the dependencies. The developers 
are sometimes not aware of using the older dependencies will result in tremendous attack. With this automatic tool,
it will support developers to solve the issues.

In Section 2, we delve into the related work on the CI/CD pipeline security. Three main 
attack surfaces within CI/CD pipeline and the counter measures are introduced here. 
Additionally, we will summarise the OWASP Top 10 CI/CD Risks. These will provide a comprehensive
foundation for our research. 

In Section 3, we will explore the realm of Software Supply Chain Security, which is the prerequisite
for understanding the key components of the Macaron Framework implemented in our research.
We dissect the Software Supply Chain, emphasizing the critical importance of provenance. 
Also, we will explain the nuanced difference between Software Bill of Materials (SBOM) and the SLSA Provenance.
Finally, we investigate the intricacies of the Build Model and the Security Levels specified by the SLSA framework.

In Section 4, we delineate our research aims and objectives. Our overarching aim is to fortify the security aspects of CI/CD pipelines. 
And our objectives include how we are going to achieve our aims. Furthermore, the current research 
progress and the research gap we find out in related works will be improved by our contribution.

Section 5 provides a detailed timetable and plan for the research project. 
We outline the key milestones, tasks, and deadlines necessary for successful project completion.

In Section 6, we offer a concise conclusion to the research proposal, summarizing our intentions and expectations.